### 2014-01-22 paper_draft_tif.tex
Added new paper-version with tif instead of png
removed \includegraphics
worked on images. submitted :)

\subsection*{Data access}
openSNP offers extensive access to the data uploaded by users. Anyone can download single genotyping files for specific users, get archives of multiple genotyping files 
grouped by phenotypic variation, or access a single download that includes all genotyping files and all phenotypic variation in a comma-separated table. The genetic data is also 
accessible through the Distributed Annotation System \cite{Dowell2001,Jenkinson2008}, which offers all data for specific chromosomes and specific positions on single chromosomes. 
An example of how the DAS can be used is implemented on openSNP, where users' genotypes are visualized inside a genome browser. So far, all chromosomal positions are based on the human reference genome NCBI36, as this is the standard reference used by DTC providers right now. \bastian{should this maybe include an image as well?}

@@

@@

\section*{Figure Legends}
\begin{figure}[!ht]
	\begin{center}
		\includegraphics[scale=0.35]{25_10_2012_Graphs/users.png}
	\end{center}
	\caption{
	{\bf Growth of openSNP-user-accounts.} The increase in numbers for users from 27.09.2011 to 27.10.2012 is shown.} 
	\label{Figure1_label}
\end{figure}
\begin{figure}[!ht]
	\begin{center}
		\includegraphics[scale=0.35]{25_10_2012_Graphs/genotypes.png}
	\end{center}
	\caption{
	{\bf Growth of available genotypings.} The increase in numbers for genotyping-files from 27.09.2011 to 27.10.2012 is shown.} 
	\label{Figure2_label}
\end{figure}
\begin{figure}[!ht]
	\begin{center}
		\includegraphics[scale=0.40]{25_10_2012_Graphs/phenotypes_vs_userphenotypes.png}
	\end{center}
	\caption{
	{\bf Development of unique phenotypes and phenotypic information over time.} The x-axis shows the time-frame from start of the project until October 2012, the left y-axis shows how many unique phenotypes have been entered, and the right y-axis shows the amount of phenotypes users entered.}
	\label{pheno}
\end{figure}

\begin{figure}[!ht]
	\begin{center}
		\includegraphics[scale=0.5]{25_10_2012_Graphs/papers_dotchart.png}
	\end{center}
	\caption{
	{\bf Distribution of annotation-sources at openSNP.} Currently, SNP-annotations from SNPedia, PLOS, Mendeley, the \emph{GET Evidence System} and the \emph{NHGRI GWAS Catalog} are being collected.}
	\label{Figure3_label}
\end{figure}

\begin{figure}[!ht]
	\begin{center}
		\includegraphics[scale=0.6]{25_10_2012_Graphs/new_pie.png}
	\end{center}
	\caption{
	{\bf Ratio of Open Access Publications.} Green pieces are Open Access. The \emph{NHGRI GWAS Catalog} doesn't give information about the Open Access status.}
	\label{oa_label}
\end{figure}

\begin{figure}[!ht]
	\begin{center}
	  \includegraphics[scale=0.3]{latest_uml.png}
	\end{center}
	\caption{
	{\bf Flow of data inside openSNP.} External databases and user-provided data are used as input. Output of data is done using the website, the \emph{Distributed Annotation System} and a JSON-API.} 
	\label{Figure4_label}
\end{figure}

>>>>

\subsection*{Data access}
openSNP offers extensive access to the data uploaded by users. Anyone can download single genotyping files for specific users, get archives of multiple genotyping files 
grouped by phenotypic variation, or access a single download that includes all genotyping files and all phenotypic variation in a comma-separated table. The genetic data is also 
accessible through the Distributed Annotation System \cite{Dowell2001,Jenkinson2008}, which offers all data for specific chromosomes and specific positions on single chromosomes. 
An example of how the DAS can be used is implemented on openSNP, where users' genotypes are visualized inside a genome browser. So far, all chromosomal positions are based on the human reference genome NCBI36, as this is the standard reference used by DTC providers right now.

@@

\subsection*{Ethics Statement}
The survey was taken anonymously by the participants and analyzed anonymously, thus IRB approval was deemed unnecessary according to US regulations in \textit{45 CFR 46.101(b)} and in accordance the Hessian data protection officer (http://www.datenschutz.hessen.de/wf001.htm\#entry2223).

@@

\section*{Figure Legends}
\begin{figure}[!ht]
	\begin{center}
	\end{center}
	\caption{
	{\bf Growth of openSNP-user-accounts.} The increase in numbers for users from 27.09.2011 to 27.10.2012 is shown.} 
	\label{Figure1_label}
\end{figure}
\begin{figure}[!ht]
	\begin{center}
	\end{center}
	\caption{
	{\bf Growth of available genotypings.} The increase in numbers for genotyping-files from 27.09.2011 to 27.10.2012 is shown.} 
	\label{Figure2_label}
\end{figure}
\begin{figure}[!ht]
	\begin{center}
	\end{center}
	\caption{
	{\bf Development of unique phenotypes and phenotypic information over time.} The x-axis shows the time-frame from start of the project until October 2012, the left y-axis shows how many unique phenotypes have been entered, and the right y-axis shows the amount of phenotypes users entered.}
	\label{pheno}
\end{figure}

\begin{figure}[!ht]
	\begin{center}
	\end{center}
	\caption{
	{\bf Distribution of annotation-sources at openSNP.} Currently, SNP-annotations from SNPedia, PLOS, Mendeley, the \emph{GET Evidence System} and the \emph{NHGRI GWAS Catalog} are being collected.}
	\label{Figure3_label}
\end{figure}

\begin{figure}[!ht]
	\begin{center}
	\end{center}
	\caption{
	{\bf Ratio of Open Access Publications.} Green pieces are Open Access. The \emph{NHGRI GWAS Catalog} doesn't give information about the Open Access status.}
	\label{oa_label}
\end{figure}

\begin{figure}[!ht]
	\begin{center}
	\end{center}
	\caption{
	{\bf Flow of data inside openSNP.} External databases and user-provided data are used as input. Output of data is done using the website, the \emph{Distributed Annotation System} and a JSON-API.} 
	\label{Figure4_label}
\end{figure}
